Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-06-20 paper/document.tex
Better hyphenation.

Apache Bookkeeper deprecated the method AbstractConfiguration.getLedgerManagerType() in release 4.2.0\footnote{\url{https://bookkeeper.apache.org/docs/r4.2.0/apidocs/deprecated-list.html}} and replaced it with AbstractConfiguration.getLedgerManagerFactoryClass(). If we look at getLedgerManagerType() we can see at the time of the start of the deprecation all instances were removed and getLedgerManagerFactoryClass() was added (Figure~\ref{fig:bookkeeper-depr}). After the deprecation, we see no more changes to getLedgerManagerType() and only some additions of getLedgerManagerFactoryClass().

>>>>

Apache Bookkeeper deprecated the method Abstract\-Configuration.\-get\-Ledger\-Manager\-Type() in release 4.2.0\footnote{\url{https://bookkeeper.apache.org/docs/r4.2.0/apidocs/deprecated-list.html}} and replaced it with Abstract\-Configuration.\-get\-Ledger\-Manager\-Factory\-Class(). If we look at get\-Ledger\-Manager\-Type() we can see at the time of the start of the deprecation all instances were removed and get\-Ledger\-Manager\-Factory\-Class() was added (Figure~\ref{fig:bookkeeper-depr}). After the deprecation, we see no more changes to get\-Ledger\-Manager\-Type() and only some additions of get\-Ledger\-Manager\-Factory\-Class().
